---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# model2fit

The goal of `model2fit` is to create an output that utilizes a visual representation that allows an analyst to explore data. Identifying trends right off the bat can help ellicit more research questions and potential areas of research.

*Note: This package is still being developed so stay tuned for more features to come*


## Installation

`model2fit` is not on CRAN yet, so the best way to install it is:

``` r
devtools::install_github("trisango/model2fit")
```

## Basic Usage

The main component thus far of this package is the `scatter_lm()` function that creates a scatter plot and its associated linear model.

This is a basic example which shows you two classes from the `palmerpenguins` dataset being tested and the resulting plot:

```{r example}
library(model2fit)
scatter_lm('body_mass_g', 'bill_length_mm', palmerpenguins::penguins)
```

## Exercise 1.1: Development of the R Package 

**1. `devtools` was loaded to set up the new package**
```{r}
#always load devtools in order to work with many features that help develop R packages
library(devtools)
```


**2. New package created in a directory on my computer**
```{r}
create_package("~/git_docs/model2fit")
```


**3. Initialize a Git repository and commit changes** 
```{r}
use_git()
```

**4. Make a new .R file for each function in your package and write the fuction in the script**
```{r}
use_r("scatter_lm")
```

```{r}
#this is the function
scatter_lm <- function(x, y, df) {
  ggplot2::ggplot(df, ggplot2::aes_string(x, y)) +
    ggplot2::geom_point(na.rm = TRUE) +
    ggplot2::geom_smooth(method = "lm", se = TRUE, colour = "purple", na.rm = TRUE)+
    ggplot2::theme_classic()
}
```

**5. Test and make scatter_lm() available for experimentation**
```{r}
load_all()
```

**6. Check that all the moving parts of this package are still work**
```{r}
check()
#Run this throughout the creation of the package to check for errors, warnings, and notes that could arise based on changes throughout the creation process.
```

**7. Description file**
Fill metadata about the package including: title, author, email, role, package description in the R script.

**8. License**
First, check which license options you have.
We use the MIT license as it is "simple and permissive" for anyone to use.
```{r}
use_mit_license("Trisa Ngo")
```

**9. Documentation**
In order to render documentation for the function `scatter_lm` in the package `model2fit` we use the `roxygen2` by clicking on Code > Insert roxygen skeleton. The title and tags such as @param and @return are described. @export is provided to allow the analyst to use the function (become an external function not just internal).

```{r}
#' Create a scatter plot and fitted linear model
#'
#' @param x Class name of x-axis of dataset.
#' @param y Class name of y-axis of dataset.
#' @param df Name of dataset.
#'
#' @return
#' A scatter plot containing a fitted linear model.
#' @export
#'
scatter_lm <- function(x, y, df) {
  ggplot2::ggplot(df, ggplot2::aes_string(x, y)) +
    ggplot2::geom_point(na.rm = TRUE) +
    ggplot2::geom_smooth(method = "lm", se = TRUE, colour = "purple", na.rm = TRUE)+
    ggplot2::theme_classic()
}
```

Then render the documentation
```{r}
document()
```

**10. Install and Restart**
Now, with a minimum viable package, in the Build tab, hit the Install and Restart button to restart and install the new package onto your computer. 

**11. Creating tests**
Declare intent to write unit tests and to use the `testthat` package for this

```{r}
use_testthat()
```

Initialize a test file and name it:
```{r}
use_test("scatter_lm")
```

I added the following test that test for:
1. Plot returns ggplot
2. Plot uses correct data
3. Printing ggplot object works

```{r}
test_that("Plot returns ggplot object",{
  test3 <- scatter_lm('body_mass_g', 'bill_length_mm', palmerpenguins::penguins)
  expect_is(test3,"ggplot")
})

test_that("Plot uses correct data", {
  test2 <- scatter_lm('body_mass_g', 'bill_length_mm', palmerpenguins::penguins)
  expect_that(palmerpenguins::penguins, equals(test2$data))
})

test_that("Printing ggplot object works", {
  test5 <- scatter_lm('body_mass_g', 'bill_length_mm', palmerpenguins::penguins)
  expect_error(print(test5), NA)
})
```

Finally you can test that your tests work:
```{r}
test()
```

**12. Dependancies**
Update code to specify dependant packages in R scrips (package::package function)

So `ggplot` updates to `ggplot2::ggplot` and `penguins` updates to `palmerpengions::penguins`


Specify which packages you will depend on so the Description File will update the Imports field. In this case, I depended on `ggplot2` and `palmerpenguins`
```{r}
use_package("ggplot2")
use_package("palmerpenguins")
```

**13. Creating a README**
Create a README.Rmd for the package that includes a description of package, installation details, and an example:
```{r}
use_readme_rmd()

#Use this to knit, run checks, and create a .md
build_readme()
```


**14. Creating and build a vignette**
```{r}
use_vignette("model2fit")

#Use this to knit the vignette
build_vignette()
```
